### 2016-11-17 paper/evaluation.tex
added reminder about piechart
wip - correlation from scatter plots

\begin{figure}[h!]
    \centering
    \includegraphics[width=0.48\textwidth]{results/plots/piechart-timecost.pdf}
    \caption{\label{fig:piechart-time} Subjects grouped by elapsed time on test
    execution ($t$): short execution ($t < 1m$), medium execution ($1m \leq t <
    5m$), and long execution ($5m \leq t$).  On the left side, results from
    sequential execution; on the right side, results from default execution.}
\end{figure}

Considering the groups \emph{medium} and \emph{long} (\Fix{X}
subjects), we investigated the relationship between the number of
tests cases and the time cost from subjects.  Figure~\ref{fig:scatters}
shows two scatter plots with We created a scatter plot for each group
and computed the correlation of time cost and number of tests.
\Fix{elaborate: As expected, Figure~\ref{fig:scatters} reveals that
the number of tests cases are not related to the elapsed time.
\Fix{explain briefly what dominates a test execution/types of tests}.
We ignored outliers for better visualization.} Results indicate that
\Fix{...conclusion...}.

>>>>

\begin{figure}[h!]
    \centering
    \includegraphics[width=0.48\textwidth]{results/plots/piechart-timecost.pdf}
    \caption{\label{fig:piechart-time} Subjects grouped by elapsed time on test
    execution ($t$): short execution ($t < 1m$), medium execution ($1m \leq t <
    5m$), and long execution ($5m \leq t$).  \Fix{On the left side, results from
    sequential execution}; on the right side, results from default execution.}
\end{figure}

Considering the groups \emph{medium} and \emph{long} (\Fix{X} subjects), we
investigated the relationship between the number of tests cases and the time
cost from subjects. \Fix{Explain what is correlation and how it is computed.}
\Fix{elaborate: As expected, Figure~\ref{fig:scatters} reveals that the number
of tests cases are not related to the elapsed time.  \Fix{explain briefly what
dominates a test execution/types of tests}.Results indicate that
\Fix{...conclusion...}.
